%-------------------------------------------------------------------------------
% Cover page
%-------------------------------------------------------------------------------
%
\makecoverpage


%-------------------------------------------------------------------------------
% Dedication (comment if none)
%-------------------------------------------------------------------------------
%
\dedication{
	{\it ``You must unlearn what you have learnt.''}\\[20pt]
	Master Yoda
}


%-------------------------------------------------------------------------------
% Abstract (English)
%-------------------------------------------------------------------------------
%
\begin{abstract}
{% Insert keywords here:
	super-lasers, space-stations, The Force, cookies.%
}%
	Access points  must work. In fact, few cryptographers would disagree with
	the emulation of robots, which embodies the technical principles of
	complexity theory. Hyp, our new application for lossless information, is the
	solution to all of these challenges.
\end{abstract}


%-------------------------------------------------------------------------------
% Abstrakt (Swedish) 
%-------------------------------------------------------------------------------
%
\begin{abstrakt}
{% Insert swedish keywords here:
	super-lasrar, rymdstationer, Kraften, kakor.%
}%
	\r{A}tkomstpunkter m\r{a}ste arbeta. I sj\"{a}lva verket skulle f\r{a}
	kryptografer h\r{a}ller inte med emulering av robotar, som
	f\"{o}rkroppsligar de tekniska principer av komplexitetsteori. Hyp, v\r{a}r
	nya applikation f\"{o}r f\"{o}rlustfri information är l\"{o}sningen på alla
	dessa utmaningar.
\end{abstrakt}


%-------------------------------------------------------------------------------
% Preface page
%-------------------------------------------------------------------------------
%
\begin{preface}
	This thesis deals with high energy super-lasers. A brief introduction on the
	basic concepts and methods is presented in the first part. The second part
	contains two articles.
	The papers are adjusted to comply with the present thesis format for
	consistency, but their contents have not been altered as compared with their
	original counterparts.
\end{preface}


%-------------------------------------------------------------------------------
% Division of work between authors
%-------------------------------------------------------------------------------
%
\begin{divisionofwork}
	The main advisor for the project is Master Obi-Wan Kenobi (OK).
	Supreme Cancellor Palpatine (DS) acts as co-advisor.

	\paperitem
		The code has been developed by Anakin Skywalker (AS).
		The paper has been written by AS and Darth Vader (DV).

	\paperitem
		The experimental set-up has been designed by DS.
		The simulations have been performed by AS using the control-code
		developed by DS.
		The paper has been written by AS and DV with feedback from OK and DS.

\end{divisionofwork}


%-------------------------------------------------------------------------------
% Additional publications (comment if none)
%-------------------------------------------------------------------------------
%
\begin{otherpublications}
	The following papers, although related, are not included in this thesis.

\paperitem{Anakin Skywalker \& Master Obi-Wan Kenobi}% Authors
          {3639}% Year
          {The light sabre: an elegant weapon for a more civilized age}% Title
          {Jedi Journal of Weapons}% Journal
          {33}% Volume
          {2}% Number
          {pp. 55--60}% Pages

\end{otherpublications}


%-------------------------------------------------------------------------------
% Conferences (comment if none)
%-------------------------------------------------------------------------------
%
\begin{conferences}
	Part of the work in this thesis has been presented at the following
        international conferences. The presenting author is underlined.

\conferenceitem{Anakin Skywalker, \underline{Darth Vader} \& Admiral Motti}% Authors
               {3639}% Year
               {Effects on breathing of underestimation of the power of The Force}% Title
               {Intergalactic Conference on Weapons and Peace}% Conference
               {Kamino}% Location

\end{conferences}


%-------------------------------------------------------------------------------
% Table of contents
%-------------------------------------------------------------------------------
%
\tableofcontents
